---
title: "BET_T2_images"
author: "Niklas Wulms"
date: "11/29/2019"
output: html_document
---


# Here we decide to use BET on the T2 images
- pydefaced images (fsl_deface removes to much relevant tissue in T2 images)
  - we use the raw version, because reorient2std and cropping does not seem to affect performance
  - we use the raw version (good, then no further preprocessing of T2 is needed)
  - and also the bias_corrected_image (gained through fsl_anat t2 pipeline)
- mri_deface does not work on T2

```{r setup, include=FALSE}
library(stringr)
library(doParallel)
library(foreach)
library(tidyr)
library(dplyr)


source("fsl_BET_T2.R")

source("../../tools/path_to_folder.R")

knitr::opts_chunk$set(echo = TRUE)

working_dir <- "/mnt/458e8a35-865f-4f0e-ab7e-8b4ac8684363/WML121_BIDS/derivatives/FSL"

knitr::opts_knit$set(root.dir = working_dir)

setwd(working_dir)
```

# Parallel setup

```{r}

# Calculate the number of cores
no_cores <- detectCores() - 1

# Initiate cluster
cl <- makeCluster(no_cores, type="FORK", outfile = "")

registerDoParallel(cl)
getDoParWorkers()
```

## Selection of the most disturbed patient preprocessings (seen above)

patient 30060, 30071, 30135, 30067

```{r}
derivatives_dir <- "/mnt/458e8a35-865f-4f0e-ab7e-8b4ac8684363/WML121_BIDS/derivatives/FSL/3-FSL_pipeline/anat_FLAIR_defaced_pydeface/"

fsl_anat_nii_selection_t2 <- data.frame(
  # raw input and first preprocs
  T2_biascorr = list.files(derivatives_dir, "T2_biascorr.nii.gz", recursive = TRUE, full.names = TRUE),
  T2 = list.files(derivatives_dir, "T2.nii.gz", recursive = TRUE, full.names = TRUE),
  stringsAsFactors = F)             

fsl_anat_nii_selection_t2  
```

```{r}
fsl_bet(fsl_anat_nii_selection_t2$T2_biascorr,
        fval=seq(0.1, 0.9, 0.1))

fsl_bet(fsl_anat_nii_selection_t2$T2,
        fval=seq(0.1, 0.9, 0.1))

```



