---
title: "fsl_flirt_t1_t2"
author: "Niklas Wulms"
date: "12/5/2019"
output: html_document
---

# Requirements

- bias corrected images (fsl_anat pipeline)
- BET images of the bias corrected images (BET fvalue: 0.4-0.5)


```{r setup, include=FALSE}
library(stringr)
library(doParallel)
library(foreach)
library(tidyr)
library(dplyr)

source("fsl_flirt.R")
source("../../tools/path_to_folder.R")

knitr::opts_chunk$set(echo = TRUE)

working_dir <- "/mnt/458e8a35-865f-4f0e-ab7e-8b4ac8684363/WML121_BIDS/derivatives/FSL"
knitr::opts_knit$set(root.dir = working_dir)
setwd(working_dir)
```



```{r}


nii_files <- data.frame(
  # raw input and first preprocs
  T1_BET_reference_pydeface_raw = list.files("/mnt/458e8a35-865f-4f0e-ab7e-8b4ac8684363/WML121_BIDS/derivatives/FSL/3-FSL_pipeline/anat_T1_defaced_pydeface",
                                             "T1_biascorr_brain.nii.gz", recursive = TRUE, full.names = TRUE),
  T1_BET_reference_fsldeface_cropped = list.files("/mnt/458e8a35-865f-4f0e-ab7e-8b4ac8684363/WML121_BIDS/derivatives/FSL/3-FSL_pipeline/anat_T1_cropped_defaced_fsl/",
                                                  "T1_biascorr_brain.nii.gz", recursive = TRUE, full.names = TRUE),
  T2_biascorr_BET  = list.files("/mnt/458e8a35-865f-4f0e-ab7e-8b4ac8684363/WML121_BIDS/derivatives/FSL/4-FSL_FLAIR_BET/anat_FLAIR_defaced_pydeface/", 
                                "0\\.4_biascorr.nii.gz", recursive = TRUE, full.names = TRUE),
  T2_biascorr  = list.files("/mnt/458e8a35-865f-4f0e-ab7e-8b4ac8684363/WML121_BIDS/derivatives/FSL/3-FSL_pipeline/anat_FLAIR_defaced_pydeface/", 
                                "T2_biascorr.nii.gz", recursive = TRUE, full.names = TRUE),
  stringsAsFactors = F)             

nii_files  
```

```{r}
fsl_flirt(input_volume = nii_files$T2_biascorr_BET,
          input_reference = nii_files$T1_BET_reference_pydeface_raw, 
          prefix = "pydeface", 
          dof = 6)

fsl_flirt(input_volume = nii_files$T2_biascorr_BET,
          input_reference = nii_files$T1_BET_reference_pydeface_raw, 
          prefix = "pydeface", 
          dof = 12)

fsl_flirt(input_volume = nii_files$T2_biascorr_BET,
          input_reference = nii_files$T1_BET_reference_fsldeface_cropped, 
          prefix = "fsldeface", 
          dof = 6)

fsl_flirt(input_volume = nii_files$T2_biascorr_BET,
          input_reference = nii_files$T1_BET_reference_fsldeface_cropped, 
          prefix = "fsldeface", 
          dof = 12)
```

## optional: bring also FLAIR Mask into T1 space using the matrix

```{r}
# not implemented
```


# Invert matrices

```{r}
mat_files <- list.files("/mnt/458e8a35-865f-4f0e-ab7e-8b4ac8684363/WML121_BIDS/derivatives/FSL/5-FSL_FLIRT", 
                                "(12|6).mat", recursive = TRUE, full.names = TRUE)

mat_files_T1_to_MNI <- list.files("/mnt/458e8a35-865f-4f0e-ab7e-8b4ac8684363/WML121_BIDS/derivatives/FSL/3-FSL_pipeline/anat_T1_defaced_pydeface/", 
                                "T1_to_MNI_lin.mat", recursive = TRUE, full.names = TRUE)
mat_files_fsldeface_06 <- list.files("/mnt/458e8a35-865f-4f0e-ab7e-8b4ac8684363/WML121_BIDS/derivatives/FSL/5-FSL_FLIRT", 
                                "_fsldeface_6.mat", recursive = TRUE, full.names = TRUE)
mat_files_fsldeface_12 <- list.files("/mnt/458e8a35-865f-4f0e-ab7e-8b4ac8684363/WML121_BIDS/derivatives/FSL/5-FSL_FLIRT", 
                                "_fsldeface_12.mat", recursive = TRUE, full.names = TRUE)
mat_files_pydeface_06 <- list.files("/mnt/458e8a35-865f-4f0e-ab7e-8b4ac8684363/WML121_BIDS/derivatives/FSL/5-FSL_FLIRT", 
                                "_pydeface_6.mat", recursive = TRUE, full.names = TRUE)
mat_files_pydeface_12 <- list.files("/mnt/458e8a35-865f-4f0e-ab7e-8b4ac8684363/WML121_BIDS/derivatives/FSL/5-FSL_FLIRT", 
                                "_pydeface_12.mat", recursive = TRUE, full.names = TRUE)
```


```{r}
# invert mat
fsl_convert_xfm(mat_files)

# concatenate mat (FLAIR_to_T1, T1_to_MNI_lin-> 1 MAT)
fsl_convert_xfm_add_masks(input_mat1 = mat_files_fsldeface_06,
                          input_mat2 = mat_files_T1_to_MNI)
fsl_convert_xfm_add_masks(input_mat1 = mat_files_fsldeface_12,
                          input_mat2 = mat_files_T1_to_MNI)
fsl_convert_xfm_add_masks(input_mat1 = mat_files_pydeface_06,
                          input_mat2 = mat_files_T1_to_MNI)
fsl_convert_xfm_add_masks(input_mat1 = mat_files_pydeface_12,
                          input_mat2 = mat_files_T1_to_MNI)
```



```{r}
# Change 6 to 06 for right order in names
mat_files <- list.files("/mnt/458e8a35-865f-4f0e-ab7e-8b4ac8684363/WML121_BIDS/derivatives/FSL/5-FSL_FLIRT", 
                                "6_inverse", recursive = TRUE, full.names = TRUE)


mat_files_06 <- str_replace(mat_files, "_6_", "_06_")
#file.rename(mat_files, mat_files_06)

mat_files <- data.frame(mat = list.files("/mnt/458e8a35-865f-4f0e-ab7e-8b4ac8684363/WML121_BIDS/derivatives/FSL/5-FSL_FLIRT", 
                                "_inverse", recursive = TRUE, full.names = TRUE),
                        stringsAsFactors = FALSE)
head(mat_files)

mat_files <- mat_files %>%
  mutate(type = str_extract(mat, "(pydeface|fsldeface)_(06|12)"),
         id = str_extract(mat, "sub-[:digit:]{5}/ses-S[:digit:]{1}")) %>%
  spread(type, mat)
```


```{r}
```

# Apply inverted matrix to T1 image, to bring it in FLAIR space

Input: 
-T1_BET pydeface raw
-T1_BET fsldeface cropped

Template:
-T2_biascorr_BET

```{r}
fsl_flirt_to_space(input_nii = nii_files$T1_BET_reference_fsldeface_cropped,
                   input_ref = nii_files$T2_biascorr_BET,
                   input_mat = mat_files$fsldeface_06)

fsl_flirt_to_space(input_nii = nii_files$T1_BET_reference_fsldeface_cropped,
                   input_ref = nii_files$T2_biascorr_BET,
                   input_mat = mat_files$fsldeface_12)

fsl_flirt_to_space(input_nii = nii_files$T1_BET_reference_pydeface_raw,
                   input_ref = nii_files$T2_biascorr_BET,
                   input_mat = mat_files$pydeface_06)

fsl_flirt_to_space(input_nii = nii_files$T1_BET_reference_pydeface_raw,
                   input_ref = nii_files$T2_biascorr_BET,
                   input_mat = mat_files$pydeface_12)
```

# Mask the T2 images, with the high-res T1 image (that is flirted to T2 space)

```{r}
nii_inverse <- data.frame(mat = list.files("/mnt/458e8a35-865f-4f0e-ab7e-8b4ac8684363/WML121_BIDS/derivatives/FSL/5-FSL_FLIRT", 
                                "T1_0\\.(0|4)_biascorr_(fsl|py)deface_(06|12)_inverse.nii.gz", recursive = TRUE, full.names = TRUE),
                        stringsAsFactors = FALSE)
head(nii_inverse)

nii_inverse <- nii_inverse %>%
  mutate(type = str_extract(mat, "(pydeface|fsldeface)_(06|12)"),
         id = str_extract(mat, "sub-[:digit:]{5}/ses-S[:digit:]{1}")) %>%
  spread(type, mat)
head(nii_inverse)
```

# The T1 image is now in T2 space (using T2_BET and T1_BET for FLIRT, as well as the inverse transformation matrix)

Now, we want to apply the T1 BET mask to the T2 images, to enhance BET quality.

```{r}
fslmaths_mask(input_nii = nii_files$T2_biascorr,
              input_mask = nii_inverse$fsldeface_06)
cat("\14")
fslmaths_mask(input_nii = nii_files$T2_biascorr,
              input_mask = nii_inverse$fsldeface_12)
cat("\14")
fslmaths_mask(input_nii = nii_files$T2_biascorr,
              input_mask = nii_inverse$pydeface_06)
cat("\14")
fslmaths_mask(input_nii = nii_files$T2_biascorr,
              input_mask = nii_inverse$pydeface_12)
cat("\14")
```

# Bringing FLAIR masks into T2_orig space

```{r}
nii_files <- data.frame(
  # raw input and first preprocs
  FLAIR = list.files("/mnt/458e8a35-865f-4f0e-ab7e-8b4ac8684363/WML121_BIDS/derivatives/FSL/3-FSL_pipeline/anat_FLAIR_defaced_pydeface/",
                                             "T2.nii.gz", recursive = TRUE, full.names = TRUE),
  FLAIR_mask = list.files("/mnt/458e8a35-865f-4f0e-ab7e-8b4ac8684363/WML121_BIDS/derivatives/manual/",
                                             "mask.nii.gz", recursive = TRUE, full.names = TRUE),
  FLAIR_to_FLAIR_orig  = list.files("/mnt/458e8a35-865f-4f0e-ab7e-8b4ac8684363/WML121_BIDS/derivatives/FSL/3-FSL_pipeline/anat_FLAIR_defaced_pydeface/", 
                                "T2_orig2std.mat", recursive = TRUE, full.names = TRUE),
  
  stringsAsFactors = F)             


output = str_replace(nii_files$FLAIR_mask, "manual", "FSL/5-FSL_FLIRT/manual") %>% str_replace("mask", "mask_T2_space") %>% str_replace("anat/", "")


```

```{r}
fsl_flirt_to_space(input_nii = nii_files$FLAIR_mask,
                   input_ref = nii_files$FLAIR,
                   input_mat = nii_files$FLAIR_to_FLAIR_orig,
                   output = output)
```

