---
title: "extract_ROI_information_FA_MD"
author: "Niklas Wulms"
date: "10/21/2019"
output: html_document
---

```{r setup, include=FALSE}
library(stringr)
library(tictoc)
library(doParallel)
library(foreach)

source("../tools/path_to_folder.R")


knitr::opts_chunk$set(echo = TRUE)

working_dir <- "/media/niklas/spaceC/WML121_BIDS_2/"
knitr::opts_knit$set(root.dir = working_dir)

setwd(working_dir)
```

# Set up parallel computing

```{r}

# Calculate the number of cores
no_cores <- detectCores() - 1

# Initiate cluster
cl <- makeCluster(no_cores, type="FORK", outfile = "")

registerDoParallel(cl)
getDoParWorkers()
```


# Find the existing FA / MD images, skeletonized too

```{r}
# error in naming files during processing in PSMD (FA named, right name is MD)

MD_native = list.files(working_dir, "temp-DTI_FA.nii.gz", recursive = TRUE, full.names = TRUE)  %>% str_replace("//", "/")
MD_native = MD_native[str_detect(MD_native, "MD")]


input_nii <- data.frame(FA_native = list.files(working_dir, "temp-DTI_FA_FA.nii.gz", recursive = TRUE, full.names = TRUE) %>% str_replace("//", "/"),
                        MD_native = MD_native,
                        
                        PSMD_txt = list.files(working_dir, "psmd.txt", recursive = TRUE, full.names = TRUE) %>% str_replace("//", "/"),
                        
                        FA_MNI152 = list.files(working_dir, "all_FA.nii.gz", recursive = TRUE, full.names = TRUE) %>% str_replace("//", "/"),
                        MD_MNI152 = list.files(working_dir, "all_MD.nii.gz", recursive = TRUE, full.names = TRUE) %>% str_replace("//", "/"),
                        
                        FA_skeleton = list.files(working_dir, "FA_skeletonised.nii.gz", recursive = TRUE, full.names = TRUE) %>% str_replace("//", "/"),
                        MD_skeleton = list.files(working_dir, "MD_skeletonised.nii.gz", recursive = TRUE, full.names = TRUE) %>% str_replace("//", "/"),
                        
                        # templates
                        FA_skeleton_mask = "/home/niklas/MATLAB_Neuroimaging/template/fsl/mean_FA_skeleton_mask.nii.gz",
                        FA_mean_mask = "/home/niklas/MATLAB_Neuroimaging/template/fsl/mean_FA_mask.nii.gz",
                        MNI_WM_mask_25 = "/home/niklas/MATLAB_Neuroimaging/template/fsl/avg152T1_white_1mm_bin_25.nii.gz",
                        MNI_WM_mask_50 = "/home/niklas/MATLAB_Neuroimaging/template/fsl/avg152T1_white_1mm_bin_50.nii.gz",
                        MNI_WM_mask_75 = "/home/niklas/MATLAB_Neuroimaging/template/fsl/avg152T1_white_1mm_bin_75.nii.gz",
                        MNI_WM_mask_100 = "/home/niklas/MATLAB_Neuroimaging/template/fsl/avg152T1_white_1mm_bin_100.nii.gz",
                        
                        # region atlas
                        MNI_atlas = "/usr/local/fsl/data/atlases/MNI/MNI-maxprob-thr0-1mm.nii.gz",
                        
                        subject = str_extract(MD_native, "[:digit:]{5}"), 
                        session = str_extract(MD_native, "ses-[:digit:]{1}"),

                        stringsAsFactors = F)

input_nii$subject_path <- sub("[/][^/]+$", "", input_nii$PSMD_txt)



input_nii

```

```{r}
output_nii <- data.frame(subject_session = paste0(input_nii$subject, "_", input_nii$session))


```


```{r}
source("extractROImean.R")
```

# Skeleton mask (applying TBSS skeleton) and ROI overlap
```{r}
extract_ROI_mean(input_nii$FA_MNI152, 
                 input_nii$FA_skeleton_mask, 
                 input_nii$MNI_atlas, 
                 input_nii$subject_path,
                 "3",
                 "MNI152_skeleton_mask_Frontal")

extract_ROI_mean(input_nii$FA_MNI152, 
                 input_nii$FA_skeleton_mask, 
                 input_nii$MNI_atlas, 
                 input_nii$subject_path,
                 "5",
                 "MNI152_skeleton_mask_Occipital")

extract_ROI_mean(input_nii$FA_MNI152, 
                 input_nii$FA_skeleton_mask, 
                 input_nii$MNI_atlas, 
                 input_nii$subject_path,
                 "6",
                 "MNI152_skeleton_mask_Parietal")

extract_ROI_mean(input_nii$FA_MNI152, 
                 input_nii$FA_skeleton_mask, 
                 input_nii$MNI_atlas, 
                 input_nii$subject_path,
                 "8",
                 "MNI152_skeleton_mask_Temporal")


```

# Mean Mask (applying Brain mask of FA processing) - like FULL brain

```{r}

extract_ROI_mean(input_nii$FA_MNI152, 
                 input_nii$FA_mean_mask, 
                 input_nii$MNI_atlas, 
                 input_nii$subject_path,
                 "3",
                 "MNI152_FA_mean_mask_Frontal")

extract_ROI_mean(input_nii$FA_MNI152, 
                 input_nii$FA_mean_mask, 
                 input_nii$MNI_atlas, 
                 input_nii$subject_path,
                 "5",
                 "MNI152_FA_mean_mask_Occipital")

extract_ROI_mean(input_nii$FA_MNI152, 
                 input_nii$FA_mean_mask, 
                 input_nii$MNI_atlas, 
                 input_nii$subject_path,
                 "6",
                 "MNI152_FA_mean_mask_Parietal")

extract_ROI_mean(input_nii$FA_MNI152, 
                 input_nii$FA_mean_mask, 
                 input_nii$MNI_atlas, 
                 input_nii$subject_path,
                 "8",
                 "MNI152_FA_mean_mask_Temporal")


```

# MNI WM Mask (applying Brain mask of MNI152 template (fsl))

the wm image was converted to 1mm resolution, then thresholded at 25, 50, 75, 100

(1) the selected ROI will be written out
(2) the ROI will be edited with another mask
  - whole-brain, 
  - wm (different thresholds)
  - skeleton
(3) this new mask will be applied to the image

```{r}

extract_ROI_mean(input_nii$FA_MNI152, 
                 input_nii$MNI_WM_mask_25, 
                 input_nii$MNI_atlas, 
                 input_nii$subject_path,
                 "3",
                 "MNI152_wm_mask_25_Frontal")

extract_ROI_mean(input_nii$FA_MNI152, 
                 input_nii$MNI_WM_mask_25, 
                 input_nii$MNI_atlas, 
                 input_nii$subject_path,
                 "5",
                 "MNI152_wm_mask_25_Occipital")

extract_ROI_mean(input_nii$FA_MNI152, 
                 input_nii$MNI_WM_mask_25, 
                 input_nii$MNI_atlas, 
                 input_nii$subject_path,
                 "6",
                 "MNI152_wm_mask_25_Parietal")

extract_ROI_mean(input_nii$FA_MNI152, 
                 input_nii$MNI_WM_mask_25, 
                 input_nii$MNI_atlas, 
                 input_nii$subject_path,
                 "8",
                 "MNI152_wm_mask_25_Temporal")

#####

extract_ROI_mean(input_nii$FA_MNI152, 
                 input_nii$MNI_WM_mask_50, 
                 input_nii$MNI_atlas, 
                 input_nii$subject_path,
                 "3",
                 "MNI152_wm_mask_50_Frontal")

extract_ROI_mean(input_nii$FA_MNI152, 
                 input_nii$MNI_WM_mask_50, 
                 input_nii$MNI_atlas, 
                 input_nii$subject_path,
                 "5",
                 "MNI152_wm_mask_50_Occipital")

extract_ROI_mean(input_nii$FA_MNI152, 
                 input_nii$MNI_WM_mask_50, 
                 input_nii$MNI_atlas, 
                 input_nii$subject_path,
                 "6",
                 "MNI152_wm_mask_50_Parietal")

extract_ROI_mean(input_nii$FA_MNI152, 
                 input_nii$MNI_WM_mask_50, 
                 input_nii$MNI_atlas, 
                 input_nii$subject_path,
                 "8",
                 "MNI152_wm_mask_50_Temporal")

####

extract_ROI_mean(input_nii$FA_MNI152, 
                 input_nii$MNI_WM_mask_75, 
                 input_nii$MNI_atlas, 
                 input_nii$subject_path,
                 "3",
                 "MNI152_wm_mask_75_Frontal")

extract_ROI_mean(input_nii$FA_MNI152, 
                 input_nii$MNI_WM_mask_75, 
                 input_nii$MNI_atlas, 
                 input_nii$subject_path,
                 "5",
                 "MNI152_wm_mask_75_Occipital")

extract_ROI_mean(input_nii$FA_MNI152, 
                 input_nii$MNI_WM_mask_75, 
                 input_nii$MNI_atlas, 
                 input_nii$subject_path,
                 "6",
                 "MNI152_wm_mask_75_Parietal")

extract_ROI_mean(input_nii$FA_MNI152, 
                 input_nii$MNI_WM_mask_75, 
                 input_nii$MNI_atlas, 
                 input_nii$subject_path,
                 "8",
                 "MNI152_wm_mask_75_Temporal")

####

extract_ROI_mean(input_nii$FA_MNI152, 
                 input_nii$MNI_WM_mask_100, 
                 input_nii$MNI_atlas, 
                 input_nii$subject_path,
                 "3",
                 "MNI152_wm_mask_100_Frontal")

extract_ROI_mean(input_nii$FA_MNI152, 
                 input_nii$MNI_WM_mask_100, 
                 input_nii$MNI_atlas, 
                 input_nii$subject_path,
                 "5",
                 "MNI152_wm_mask_100_Occipital")

extract_ROI_mean(input_nii$FA_MNI152, 
                 input_nii$MNI_WM_mask_100, 
                 input_nii$MNI_atlas, 
                 input_nii$subject_path,
                 "6",
                 "MNI152_wm_mask_100_Parietal")

extract_ROI_mean(input_nii$FA_MNI152, 
                 input_nii$MNI_WM_mask_100, 
                 input_nii$MNI_atlas, 
                 input_nii$subject_path,
                 "8",
                 "MNI152_wm_mask_100_Temporal")


```




```{r}
library(tidyr)

roi_txt <- list.files(path = working_dir,
           pattern = ".txt", recursive = TRUE) %>% data.frame(files = ., stringsAsFactors = FALSE) %>%
  filter(str_detect(files, "ROI|psmd.txt") == 1)

roi <- roi_txt %>%
  separate(files, into = c("base", "subject", "session", "type", "ROI", "file"), sep = "/", fill = "left") %>%
  cbind(roi_txt) %>%
  filter(ROI %in% c("ROI")) %>%
  mutate(atlas = str_extract(file, "MNI152"),
         mask = str_extract(file, "(FA_mean|skeleton|wm)_(mask_(25|50|75|100)|mask)"),
         region = str_extract(file, "Frontal|Parietal|Temporal|Occipital"),
         value = unlist(lapply(roi$files, scan, what = numeric(), quiet = TRUE))) %>%
  select(files, everything())


read_psmd <- function(input_txt) {
    PSMD_value <- read.delim(input_txt, stringsAsFactors = FALSE) %>% as.character(.) %>% str_extract("[:digit:]{1}.[:digit:]+")
    return(PSMD_value)
    }


roi$psmd_value <- lapply(input_nii$PSMD_txt, read_psmd)
```

```{r}
roi_wide <- roi %>%
  select(subject, session, atlas, mask, region, value) %>%
  spread(region, value) %>%
  arrange(mask)

```

```{r}
library(ggplot2)
library(forcats)


roi$mask <- fct_relevel(as.factor(roi$mask), c("FA_mean_mask", "wm_mask_25", "wm_mask_50", "wm_mask_75", "wm_mask_100", "skeleton_mask"))

roi %>%
  select(subject, session, atlas, mask, region, value) %>%
  ggplot(aes(x = session, y = value)) +
  geom_boxplot() +
  facet_grid(region ~ mask)
```

