---
title: "BIANCA_gender_age_models"
author: "Niklas Wulms"
date: "1/6/2020"
output: html_document
---


```{r setup, include=FALSE}
library(stringr)
library(doParallel)
library(foreach)
library(tidyr)
library(dplyr)

# source("/anat/fsl/fsl_BIANCA.R")
source("/home/niklas/Coding/bidirect-neuroimaging-processing/tools/path_to_folder.R")
source("/home/niklas/Coding/bidirect-neuroimaging-processing/anat/fsl/fsl_BIANCA.R")

knitr::opts_chunk$set(echo = TRUE)

working_dir <- "/mnt/458e8a35-865f-4f0e-ab7e-8b4ac8684363/WML121_BIDS/derivatives/FSL"
knitr::opts_knit$set(root.dir = working_dir)
```






## Models based on properties (age, gender)

```{r}
subject_data_s4 <- read.table("/home/niklas/Dropbox/White_Matter_Project/WML_Paper_Code/wml_paper/export/wml_121.txt", header = TRUE)

subject_data_s4 <- subject_data_s4 %>%
  select(Patientennummer, Survey, Alter, Geschlecht) %>%
  mutate(id = as.character(Patientennummer),
         ses = str_replace(as.character(Survey), "Follow_Up_2", "ses-S4"),
         age_class = cut(Alter, 
                         breaks = c(40, 45, 50, 55, 60, 65, 70, 75),
                         labels=c("40-44", "45-49", "50-54", "55-59", "60-64", "65-69", "70-74"))) %>%
  select(-Patientennummer, -Survey) %>% left_join(pydeface_06)

subject_data_s0 <- read.table("/home/niklas/Dropbox/White_Matter_Project/WML_Paper_Code/wml_paper/export/wml_80.txt", header = TRUE)

subject_data_s0 <- subject_data_s0 %>%
  select(Patientennummer, Survey, Alter, Geschlecht) %>%
  mutate(id = as.character(Patientennummer),
         ses = str_replace(as.character(Survey), "Baseline", "ses-S0") %>% str_replace("Follow_Up_2", "ses-S4"),
         age_class = cut(Alter, 
                         breaks = c(40, 45, 50, 55, 60, 65, 70, 75),
                         labels=c("40-44", "45-49", "50-54", "55-59", "60-64", "65-69", "70-74"))) %>%
  select(-Patientennummer, -Survey) %>% left_join(pydeface_06)

table(subject_data_s0$age_class, subject_data_s0$Geschlecht)


subject_data <- union(subject_data_s0, subject_data_s4)

```

```{r}
library(ggplot2)
ggplot(subject_data_s0, aes(x = Alter)) +
  geom_histogram(bins = 5)
```


# Permutation loop sampling from gender and class groups one subject (14 in total)

All observations drawn from S0!

```{r}
dir.create("6-BIANCA/permutation_age_class_gender/txt_files/train")
dir.create("6-BIANCA/permutation_age_class_gender/txt_files/test")
set.seed(142)

# Here from each gender (2) and age-class (14) one subject is drawn

runs = 100

# due to needed subject to predict argument in BIANCA function, 
# we add to each set one subject, that the tool is applied on,
# and to get the classifier saved

for (i in 1:runs) {
  filename_train = paste0("6-BIANCA/permutation_age_class_gender/txt_files/train/", "random_draw_train_", sprintf("%03d", i), ".txt")
  filename_test = paste0("6-BIANCA/permutation_age_class_gender/txt_files/test/", "random_draw_test_", sprintf("%03d", i), ".txt")
  random_train <- subject_data %>%
    filter(ses == "ses-S0") %>%
    group_by(Geschlecht, age_class) %>%
    sample_n(1, replace = FALSE) %>% 
    ungroup() 
  
  
  
  # containing all subjects at S4 and S0 only the ones, that are not selected by random train
  random_test <- anti_join(subject_data, random_train, 
                           by = c("Alter", "Geschlecht", "id", "ses", "age_class", "FLAIR_BET", 
                                  "T1_BET_to_FLAIR", "FLAIR_to_MNI", "mask", "output")) 
  
  # containing a subject not used in the train set at S0 or S4 for LOO in Bianca function
  random_subject <- random_test %>%
    filter(!id %in% random_train) %>%
    sample_n(1)
  
  testing_random_subject <- anti_join(random_subject, random_train, 
                                      by = c("Alter", "Geschlecht", "id", "ses", "age_class", "FLAIR_BET", 
                                             "T1_BET_to_FLAIR", "FLAIR_to_MNI", "mask", "output")) %>% nrow()
  # Testing, if subject used for prediction is really not in the training data. The printed TRUE states, that this is done!
  print(paste0("Random subject? == ", testing_random_subject == 1,
               " N of random subject (1)? == ", nrow(random_subject),
               "  Length Training data: ", nrow(random_train),
               "  Length Test data: ", nrow(random_test)))
  
  # Write out the masterfiles for BIANCA
  random_train %>%
    rbind(random_subject) %>%
    select(FLAIR_BET, T1_BET_to_FLAIR, FLAIR_to_MNI, mask) %>% 
    write.table(file=filename_train, quote=FALSE, sep='\t', col.names = FALSE, row.names = FALSE)
  
  #random_train %>% select(id, ses) %>% print()  
  
  random_test %>%
    select(FLAIR_BET, T1_BET_to_FLAIR, FLAIR_to_MNI) %>%
    write.table(file=filename_test, quote=FALSE, sep='\t', col.names = FALSE, row.names = FALSE)
}
```

```{r}
dir.create("6-BIANCA/permutation_age_class_gender/txt_files/trained_classifier")
training_sets = list.files("6-BIANCA/permutation_age_class_gender/txt_files/train/", "train", full.names = TRUE)
trained_algorithms = str_replace(training_sets, "/train/", "/trained_classifier") %>% str_replace("\\.txt", "_model")


```

# Train using the masterfiles

```{r}
output = str_replace(trained_algorithms, "$", ".nii.gz")

train_bianca(training_sets, output_name = output, output_classifier = trained_algorithms)
# These are only here to apply (also listed above!)

```

# Here I need to work on:
To open each file, read out the file to segment - get the filename and make it to an output name. ID, session need to be exact! THis needs a solution before applying the trained classifiers!

## Apply the trained classifiers on the test sets
```{r}
trained_models = list.files("6-BIANCA/permutation_age_class_gender/txt_files/trained_classifier/", "model$", full.names = TRUE)
trained_models <- paste0(working_dir, "/", trained_models)
test_sets = list.files("6-BIANCA/permutation_age_class_gender/txt_files/test/", "test", full.names = TRUE)
test_sets <- paste0(working_dir, "/", test_sets)

```



```{r}
application_bianca_classifiers <- function(trained_models, test_sets){
  for (i in 1:length(trained_models)) {
    # Clear terminal
    cat("\014")
    
    # Creation of output folders
    output_folder <- str_replace(trained_models[i], "trained_classifier/", "trained_classifier_output")
    print(output_folder)
    # Reading in of file list for model application
    output_masks <- read.table(test_sets[i], sep = '\t', header = FALSE)[,1] %>% as.character() %>%
      str_replace("/mnt/458e8a35-865f-4f0e-ab7e-8b4ac8684363/WML121_BIDS/derivatives/FSL/5-FSL_FLIRT/anat_FLAIR_defaced_pydeface/", output_folder) %>% 
      str_replace(".nii.gz", "_BIANCA_mask")
    # print(length(output_masks))
    # print(head(output_masks))
    
    initialize_parallel(not_use = 5)
    
    
    #for (j in 1:length(output_masks)){
    

    foreach (j = 1:length(output_masks)) %dopar% {
      path_to_folder(output_masks[j])
      cat("\014")

      command <- paste0("bianca --singlefile=", test_sets[i], 
                        " --loadclassifierdata=", trained_models[i],
                        " --brainmaskfeaturenum=1 --querysubjectnum=", j,
                        " --featuresubset=1,2 --matfeaturenum=3 -o ", output_masks[j] 
                        #" -v"
                        )
      print(command)
      if(file.exists(paste0(output_masks[j], ".nii.gz")) == 0) {
        system("clear")
        system(command)
      }
    }
  }
}
  

application_bianca_classifiers(trained_models, test_sets)
```

# Extraction of quality metrices

```{r}
files <- data.frame(masks = list.files("/mnt/458e8a35-865f-4f0e-ab7e-8b4ac8684363/WML121_BIDS/derivatives/FSL/6-BIANCA/permutation_age_class_gender/txt_files/trained_classifier_output/", "mask.nii.gz", recursive = TRUE, full.names = TRUE) %>% as.character())

files <- files %>%
  mutate(id = str_extract(masks, "sub-[:digit:]{5}") %>% str_extract("[:digit:]{5}"),
         ses = str_extract(masks, "ses-S[:digit:]{1}"),
         model = str_extract(masks, "train_[:digit:]{3}_model")
         )

mask <- data.frame(manual_masks = list.files("/mnt/458e8a35-865f-4f0e-ab7e-8b4ac8684363/WML121_BIDS/derivatives/FSL/5-FSL_FLIRT/manual/", 
                                "mask_T2_space.nii.gz", recursive = TRUE, full.names = TRUE) %>% as.character())
mask <- mask %>%
  mutate(id = str_extract(manual_masks, "sub-[:digit:]{5}") %>% str_extract("[:digit:]{5}"),
         ses = str_extract(manual_masks, "ses-S[:digit:]{1}"))

thresh <- seq(0.0, 1, 0.1)
thresh

files_expand <- left_join(files, mask) %>%
  mutate(output = str_replace(masks, ".nii.gz", ".txt")) %>%
  group_by_all() %>% 
  expand(thresh) %>% ungroup() %>%
  mutate(output_volume_file = str_replace(output, ".txt$", paste0("_bianca_volume_thresh_", thresh, ".txt")),
         output_performance_file = str_replace(output_volume_file, "_bianca_volume_thresh_", "_bianca_performance_thresh_"))
```


# Write out the mask volumes

```{r}
bianca_cluster_info(lesionmask = files_expand$masks, 
                    threshold = files_expand$thresh,
                    output_name = files_expand$output_volume_file)
```

```{r}
bianca_performance(lesionmask = files_expand$masks, 
                   threshold = files_expand$thresh, 
                   manualmask = files_expand$manual_masks,
                   output_name = files_expand$output_performance_file)
```

