---
title: "Preprocessing_QC"
author: "Niklas Wulms"
date: "10/16/2019"
output: html_document
---
```{r setup, include=FALSE}
library(stringr)
library(doParallel)
library(foreach)
library(tidyr)
library(dplyr)

source("../2-image_quality/qc_fsleyes.R")
source("../tools/path_to_folder.R")

knitr::opts_chunk$set(echo = TRUE)

working_dir <- "/media/niklas/spaceC/WML121_BIDS"

knitr::opts_knit$set(root.dir = working_dir)

setwd(working_dir)
```

# Parallel setup

```{r}

# Calculate the number of cores
no_cores <- detectCores() - 1

# Initiate cluster
cl <- makeCluster(no_cores, type="FORK", outfile = "")

registerDoParallel(cl)
getDoParWorkers()
```

# input images

```{r}

derivatives_dir <- "/media/niklas/spaceC/WML121_BIDS/derivatives/FSL/3-FSL_pipeline/"

scan <- "T1_fast_restore.nii.gz"

fsl_anat_nii <- data.frame(
  # raw input and first preprocs
  T1 = list.files(paste0(derivatives_dir, "anat_T1"), scan, recursive = T, full.names = T),
  T1_reorient2std = list.files(paste0(derivatives_dir, "anat_T1_crop"), scan, recursive = T, full.names = T),
  T1_cropped = list.files(paste0(derivatives_dir, "anat_T1_reorient2std"), scan, recursive = T, full.names = T),
  # defacing
  T1_defaced_mri = list.files(paste0(derivatives_dir, "anat_T1_defaced_mri_deface"), scan, recursive = T, full.names = T),
  T1_defaced_pydeface = list.files(paste0(derivatives_dir, "anat_T1_defaced_pydeface"), scan, recursive = T, full.names = T),
  
  T1_reorient2std_defaced_mri = list.files(paste0(derivatives_dir, "anat_T1_r2std_defaced_mri_deface"), scan, recursive = T, full.names = T),
  T1_reorient2std_defaced_pydeface = list.files(paste0(derivatives_dir, "anat_T1_r2std_defaced_pydeface"), scan, recursive = T, full.names = T),
  
  T1_cropped_defaced_mri = list.files(paste0(derivatives_dir, "anat_T1_cropped_defaced_mri_deface"), scan, recursive = T, full.names = T),
  T1_cropped_defaced_pydeface = list.files(paste0(derivatives_dir, "anat_T1_cropped_defaced_pydeface"), scan, recursive = T, full.names = T),
  
  stringsAsFactors = F
)

head(fsl_anat_nii)
str(fsl_anat_nii)
```

```{r}
fsl_anat_png <- data.frame(
  T1_raw = str_replace(input_nii$T1_defaced_pydeface, "derivatives/FSL/2-Anonymize/sub-[:digit:]{5}/ses-S[:digit:]{1}/anat", "qualitycontrol/3-fsl_anat/raw") %>% 
    str_replace(".nii.gz", "_comp_fsl_anat_raw.jpg"),
  T1_mri_deface = str_replace(input_nii$T1_defaced_mri, "derivatives/FSL/2-Anonymize/sub-[:digit:]{5}/ses-S[:digit:]{1}/anat", "qualitycontrol/3-fsl_anat/mri_deface") %>% 
    str_replace(".nii.gz", "_comp_fsl_anat_mri_deface.jpg"),
  T1_pydeface = str_replace(input_nii$T1_defaced_pydeface, "derivatives/FSL/2-Anonymize/sub-[:digit:]{5}/ses-S[:digit:]{1}/anat", "qualitycontrol/3-fsl_anat/pydeface") %>% 
    str_replace(".nii.gz", "_comp_fsl_anat_pydeface.jpg"),
  
  T1_raw2 = str_replace(input_nii$T1_defaced_pydeface, "derivatives/FSL/2-Anonymize/sub-[:digit:]{5}/ses-S[:digit:]{1}/anat", "qualitycontrol/3-fsl_anat/T1") %>% 
    str_replace(".nii.gz", "_comp_fsl_anat_T1_raw.jpg"),
  T1_reorient2std = str_replace(input_nii$T1_defaced_mri, "derivatives/FSL/2-Anonymize/sub-[:digit:]{5}/ses-S[:digit:]{1}/anat", "qualitycontrol/3-fsl_anat/T1") %>% 
    str_replace(".nii.gz", "_comp_fsl_anat_T1_reorient.jpg"),
  T1_cropped = str_replace(input_nii$T1_defaced_pydeface, "derivatives/FSL/2-Anonymize/sub-[:digit:]{5}/ses-S[:digit:]{1}/anat", "qualitycontrol/3-fsl_anat/T1") %>% 
    str_replace(".nii.gz", "_comp_fsl_anat_T1_cropped.jpg"),
  
  stringsAsFactors = FALSE
)

dir.create("qualitycontrol/3-fsl_anat/raw", recursive = TRUE)
dir.create("qualitycontrol/3-fsl_anat/mri_deface", recursive = TRUE)
dir.create("qualitycontrol/3-fsl_anat/pydeface", recursive = TRUE)

dir.create("qualitycontrol/3-fsl_anat/T1", recursive = TRUE)


```

# Create FSLeyes images for each subject to look for best performing data, when using Pydeface or MRI_deface
- based on input data

# Comparison of the input_data type
```{r}
qc_fsleyes_defacing(fsl_anat_nii$T1_reorient2std, fsl_anat_nii$T1, fsl_anat_nii$T1_cropped, 
                    output_t1 = fsl_anat_png$T1_raw,
                    slice_spacing = 6.5)

qc_fsleyes_defacing(fsl_anat_nii$T1_reorient2std_defaced_mri, fsl_anat_nii$T1_defaced_mri, fsl_anat_nii$T1_cropped_defaced_mri, 
                    output_t1 = fsl_anat_png$T1_mri_deface,
                    slice_spacing = 6.5)

qc_fsleyes_defacing(fsl_anat_nii$T1_reorient2std_defaced_pydeface, fsl_anat_nii$T1_pydeface, fsl_anat_nii$T1_cropped_defaced_pydeface, 
                    output_t1 = fsl_anat_png$T1_pydeface,
                    slice_spacing = 6.5)
```

# Choose the best data of Pydeface and MRI_deface and compare both with other
- based on algorithms

# Comparison of the defacing influence

```{r}
qc_fsleyes_defacing(fsl_anat_nii$T1_reorient2std, fsl_anat_nii$T1_reorient2std_defaced_mri, fsl_anat_nii$T1_reorient2std_defaced_pydeface, 
                    output_t1 = fsl_anat_png$T1_raw2,
                    slice_spacing = 6.5)

qc_fsleyes_defacing(fsl_anat_nii$T1_reorient2std, fsl_anat_nii$T1_defaced_mri, fsl_anat_nii$T1_pydeface, 
                    output_t1 = fsl_anat_png$T1_reorient2std,
                    slice_spacing = 6.5)

qc_fsleyes_defacing(fsl_anat_nii$T1_cropped, fsl_anat_nii$T1_cropped_defaced_mri, fsl_anat_nii$T1_cropped_defaced_pydeface, 
                    output_t1 = fsl_anat_png$T1_cropped,
                    slice_spacing = 6.5)
```

## Selection of the most disturbed patient preprocessings (seen above)

patient 30060, 30071, 30135, 30067

```{r}
fsl_anat_nii_selection <- data.frame(
  # raw input and first preprocs
  T1_biascorr = list.files(derivatives_dir, "T1_biascorr.nii.gz", recursive = TRUE, full.names = TRUE),
  T1_brain_mask = list.files(derivatives_dir, "T1_biascorr_brain_mask.nii.gz", recursive = TRUE, full.names = TRUE),
  
  stringsAsFactors = F
) %>%
  mutate(id = str_extract(T1_biascorr, "[:digit:]{5}")) %>%
  filter(id %in% c("30060", "30071", "30135", "30067")) %>%
  mutate(output = str_replace(T1_brain_mask, "//", "/") %>% str_replace("derivatives/FSL/3-FSL_pipeline/", "qualitycontrol/3-fsl_anat_selection/") %>%
           str_replace("/(?=sub-[:digit:]{5})", "_") %>% str_replace("/(?=ses-S[:digit:]{1})", "_") %>% str_replace("/anat.anat/", "_") %>% str_replace("nii.gz", "png")
           
           )

```

```{r}
qc_fsleyes_defacing_1(fsl_anat_nii_selection$T1_biascorr, fsl_anat_nii_selection$T1_brain_mask,
                      output_t1 = fsl_anat_nii_selection$output,
                      slice_spacing = 6.5)
```


```{r}
fsl_anat_selection_pngs <- data.frame(
  pngs = list.files(paste0(working_dir, "/qualitycontrol"), "png", recursive = TRUE, full.names = TRUE),
  stringsAsFactors = FALSE
)
```

```{r}
fsl_anat_selection_pngs <- fsl_anat_selection_pngs %>%
  mutate(id = str_extract(pngs, "[:digit:]{5}"),
         ses = str_extract(pngs, "ses-S[:digit:]{1}"),
         sequence = str_extract(pngs, "[:graph:]*(?=_sub-[:digit:]{5})") %>% str_replace(paste0(working_dir, "/qualitycontrol/3-fsl_anat_selection/anat_"), "") %>% as.factor()
  )

test <- fsl_anat_selection_pngs %>%
  pivot_wider(names_from = sequence, values_from = pngs) %>%
  mutate(out = paste0(id, "_", ses, ".png"))
```


```{r}
collage_nine(test$T1, test$T1_defaced_mri_deface, test$T1_defaced_pydeface,
             test$T1_reorient2std, test$T1_r2std_defaced_mri_deface, test$T1_r2std_defaced_pydeface,
             test$T1_crop, test$T1_cropped_defaced_mri_deface, test$T1_cropped_defaced_pydeface,
             test$out, high_res = TRUE, low_res = TRUE)
```

