---
title: "Preprocessing_QC"
author: "Niklas Wulms"
date: "10/16/2019"
output: html_document
---
```{r setup, include=FALSE}
library(stringr)
library(doParallel)
library(foreach)
library(tidyr)
library(dplyr)

source("../2-image_quality/qc_fsleyes.R")
source("../tools/path_to_folder.R")

knitr::opts_chunk$set(echo = TRUE)

working_dir <- "/media/niklas/spaceC/WML121_BIDS"

knitr::opts_knit$set(root.dir = working_dir)

setwd(working_dir)
```

# Parallel setup

```{r}

# Calculate the number of cores
no_cores <- detectCores() - 1

# Initiate cluster
cl <- makeCluster(no_cores, type="FORK", outfile = "")

registerDoParallel(cl)
getDoParWorkers()
```

# input images

```{r}

derivatives_dir <- "/media/niklas/spaceC/WML121_BIDS/derivatives/FSL/3-FSL_pipeline/"

scan <- "T1_fast_restore.nii.gz"

fsl_anat_nii <- data.frame(
  # raw input and first preprocs
  T1 = list.files(paste0(derivatives_dir, "anat_T1_BET_05"), scan, recursive = T, full.names = T),
  T1_reorient2std = list.files(paste0(derivatives_dir, "anat_T1_crop_BET_05"), scan, recursive = T, full.names = T),
  T1_cropped = list.files(paste0(derivatives_dir, "anat_T1_reorient2std_BET_05"), scan, recursive = T, full.names = T),
  # defacing
  T1_defaced_mri = list.files(paste0(derivatives_dir, "anat_T1_defaced_mri_deface_BET_05"), scan, recursive = T, full.names = T),
  T1_defaced_pydeface = list.files(paste0(derivatives_dir, "anat_T1_defaced_pydeface_BET_05"), scan, recursive = T, full.names = T),
  
  T1_reorient2std_defaced_mri = list.files(paste0(derivatives_dir, "anat_T1_r2std_defaced_mri_deface_BET_05"), scan, recursive = T, full.names = T),
  T1_reorient2std_defaced_pydeface = list.files(paste0(derivatives_dir, "anat_T1_r2std_defaced_pydeface_BET_05"), scan, recursive = T, full.names = T),
  
  T1_cropped_defaced_mri = list.files(paste0(derivatives_dir, "anat_T1_cropped_defaced_mri_deface_BET_05"), scan, recursive = T, full.names = T),
  T1_cropped_defaced_pydeface = list.files(paste0(derivatives_dir, "anat_T1_cropped_defaced_pydeface_BET_05"), scan, recursive = T, full.names = T),
  
  stringsAsFactors = F
)

head(fsl_anat_nii)
str(fsl_anat_nii)
```

```{r}
fsl_anat_png <- data.frame(
  T1_raw = str_replace(fsl_anat_nii$T1_defaced_pydeface, "derivatives/FSL/3-FSL_pipeline/anat_T1_defaced_pydeface_BET_05", "qualitycontrol/3-fsl_anat/raw_BET_05") %>% str_replace("anat.anat", "") %>% str_replace_all("(?<=ses-S[:digit:]{1})//|(?<=sub-[:digit:]{5})/", "_") %>% str_replace(".nii.gz", "_comp_fsl_anat_raw.jpg"),
  T1_mri_deface = str_replace(fsl_anat_nii$T1_defaced_mri, "derivatives/FSL/3-FSL_pipeline/anat_T1_defaced_mri_deface_BET_05", "qualitycontrol/3-fsl_anat/mri_deface_BET_05") %>% str_replace("anat.anat", "") %>% str_replace_all("(?<=ses-S[:digit:]{1})//|(?<=sub-[:digit:]{5})/", "_") %>%  str_replace(".nii.gz", "_comp_fsl_anat_mri_deface.jpg"),
  T1_pydeface = str_replace(fsl_anat_nii$T1_defaced_pydeface, "derivatives/FSL/3-FSL_pipeline/anat_T1_defaced_pydeface_BET_05", "qualitycontrol/3-fsl_anat/pydeface_BET_05") %>% str_replace("anat.anat", "") %>% str_replace_all("(?<=ses-S[:digit:]{1})//|(?<=sub-[:digit:]{5})/", "_")%>%   str_replace(".nii.gz", "_comp_fsl_anat_pydeface.jpg"),
  
  T1_raw2 = str_replace(fsl_anat_nii$T1_defaced_pydeface, "derivatives/FSL/3-FSL_pipeline/anat_T1_defaced_pydeface_BET_05", "qualitycontrol/3-fsl_anat/T1_BET_05") %>% str_replace("anat.anat", "") %>% str_replace_all("(?<=ses-S[:digit:]{1})//|(?<=sub-[:digit:]{5})/", "_")%>%   str_replace(".nii.gz", "_comp_fsl_anat_T1_raw.jpg"),
  T1_reorient2std = str_replace(fsl_anat_nii$T1_defaced_mri, "derivatives/FSL/3-FSL_pipeline/anat_T1_defaced_mri_deface_BET_05", "qualitycontrol/3-fsl_anat/T1_BET_05") %>% str_replace("anat.anat", "") %>% str_replace_all("(?<=ses-S[:digit:]{1})//|(?<=sub-[:digit:]{5})/", "_")%>% str_replace(".nii.gz", "_comp_fsl_anat_T1_reorient.jpg"),
  T1_cropped = str_replace(fsl_anat_nii$T1_defaced_pydeface, "derivatives/FSL/3-FSL_pipeline/anat_T1_defaced_pydeface_BET_05", "qualitycontrol/3-fsl_anat/T1_BET_05") %>% str_replace("anat.anat", "") %>% str_replace_all("(?<=ses-S[:digit:]{1})//|(?<=sub-[:digit:]{5})/", "_")%>% str_replace(".nii.gz", "_comp_fsl_anat_T1_cropped.jpg"),
  
  stringsAsFactors = FALSE
)

dir.create("qualitycontrol/3-fsl_anat/raw_BET_05", recursive = TRUE)
dir.create("qualitycontrol/3-fsl_anat/mri_deface_BET_05", recursive = TRUE)
dir.create("qualitycontrol/3-fsl_anat/pydeface_BET_05", recursive = TRUE)
dir.create("qualitycontrol/3-fsl_anat/T1_BET_05", recursive = TRUE)


head(fsl_anat_png)

```

# Create FSLeyes images for each subject to look for best performing data, when using Pydeface or MRI_deface
- based on input data

# Comparison of the input_data type
```{r}
qc_fsleyes_defacing(fsl_anat_nii$T1_reorient2std, fsl_anat_nii$T1, fsl_anat_nii$T1_cropped, 
                    output_t1 = fsl_anat_png$T1_raw,
                    slice_spacing = 6.5)

qc_fsleyes_defacing(fsl_anat_nii$T1_reorient2std_defaced_mri, fsl_anat_nii$T1_defaced_mri, fsl_anat_nii$T1_cropped_defaced_mri, 
                    output_t1 = fsl_anat_png$T1_mri_deface,
                    slice_spacing = 6.5)

qc_fsleyes_defacing(fsl_anat_nii$T1_reorient2std_defaced_pydeface, fsl_anat_nii$T1_pydeface, fsl_anat_nii$T1_cropped_defaced_pydeface, 
                    output_t1 = fsl_anat_png$T1_pydeface,
                    slice_spacing = 6.5)
```

# Choose the best data of Pydeface and MRI_deface and compare both with other
- based on algorithms

# Comparison of the defacing influence

```{r}
qc_fsleyes_defacing(fsl_anat_nii$T1_reorient2std, fsl_anat_nii$T1_reorient2std_defaced_mri, fsl_anat_nii$T1_reorient2std_defaced_pydeface, 
                    output_t1 = fsl_anat_png$T1_raw2,
                    slice_spacing = 6.5)

qc_fsleyes_defacing(fsl_anat_nii$T1_reorient2std, fsl_anat_nii$T1_defaced_mri, fsl_anat_nii$T1_pydeface, 
                    output_t1 = fsl_anat_png$T1_reorient2std,
                    slice_spacing = 6.5)

qc_fsleyes_defacing(fsl_anat_nii$T1_cropped, fsl_anat_nii$T1_cropped_defaced_mri, fsl_anat_nii$T1_cropped_defaced_pydeface, 
                    output_t1 = fsl_anat_png$T1_cropped,
                    slice_spacing = 6.5)
```

## Selection of the most disturbed patient preprocessings (seen above)

patient 30060, 30071, 30135, 30067

```{r}
fsl_anat_nii_selection <- data.frame(
  # raw input and first preprocs
  T1_biascorr = list.files(derivatives_dir, "T1_biascorr.nii.gz", recursive = TRUE, full.names = TRUE),
  T1_brain_mask = list.files(derivatives_dir, "T1_biascorr_brain_mask.nii.gz", recursive = TRUE, full.names = TRUE),
  
  stringsAsFactors = F
) %>%
  mutate(id = str_extract(T1_biascorr, "[:digit:]{5}")) %>%
  filter(id %in% c("30060", "30071", "30135", "30067")) %>%
  filter(str_detect(T1_biascorr, "BET_05") == 1) %>%
  mutate(output = str_replace(T1_brain_mask, "//", "/") %>% str_replace("derivatives/FSL/3-FSL_pipeline/", "qualitycontrol/3-fsl_anat_selection_BET_05/") %>%
           str_replace("/(?=sub-[:digit:]{5})", "_") %>% str_replace("/(?=ses-S[:digit:]{1})", "_") %>% str_replace("/anat.anat/", "_") %>% str_replace("nii.gz", "png")
           
           )

```

```{r}
dir.create("/media/niklas/spaceC/WML121_BIDS/qualitycontrol/3-fsl_anat_selection_BET_05")

qc_fsleyes_defacing_1(fsl_anat_nii_selection$T1_biascorr, fsl_anat_nii_selection$T1_brain_mask,
                      output_t1 = fsl_anat_nii_selection$output,
                      slice_spacing = 6.5)
```


```{r}
fsl_anat_selection_pngs <- data.frame(
  pngs = list.files(paste0(working_dir, "/qualitycontrol/3-fsl_anat_selection_BET_05"), "png", recursive = TRUE, full.names = TRUE),
  stringsAsFactors = FALSE
)
```

```{r}
fsl_anat_selection_pngs <- fsl_anat_selection_pngs %>%
  mutate(id = str_extract(pngs, "[:digit:]{5}"),
         ses = str_extract(pngs, "ses-S[:digit:]{1}"),
         sequence = str_extract(pngs, "[:graph:]*(?=_sub-[:digit:]{5})") %>% str_replace(paste0(working_dir, "/qualitycontrol/3-fsl_anat_selection_BET_05/anat_"), "") %>% as.factor()
  ) %>%
  filter(str_detect(sequence, "BET_05") == 1)

test <- fsl_anat_selection_pngs %>%
  pivot_wider(names_from = sequence, values_from = pngs) %>%
  mutate(out = paste0(id, "_", ses, ".png"))
```


```{r}
setwd("qualitycontrol/3-fsl_anat_selection_BET_05")

collage_nine(test$T1_BET_05, test$T1_defaced_mri_deface_BET_05, test$T1_defaced_pydeface_BET_05,
             test$T1_reorient2std_BET_05, test$T1_r2std_defaced_mri_deface_BET_05, test$T1_r2std_defaced_pydeface_BET_05,
             test$T1_crop_BET_05, test$T1_cropped_defaced_mri_deface_BET_05, test$T1_cropped_defaced_pydeface_BET_05,
             test$out, h_res = TRUE, l_res = TRUE)
```


# Sven Niklas Idee

```{r}
mask <-fsl_anat_nii_selection$T1_brain_mask[1]


mask_volume <- function(binary_mask){
  
  output <- system(paste0(
    "fslstats ", binary_mask, " -V"
  ), intern = TRUE)

}

out_test_vox <- mask_volume(mask)


lapply(fsl_anat_nii_selection$T1_brain_mask, mask_volume)
```

```{r}
fsl_anat_nii_selection <- fsl_anat_nii_selection %>%
  select(T1_brain_mask, id) %>%
  mutate(session = str_extract(T1_brain_mask, "ses-S(0|4)"))

fsl_anat_nii_selection$voxel_volume <- lapply(fsl_anat_nii_selection$T1_brain_mask, mask_volume)


fsl_anat_nii_selection$voxel_n <- str_extract(fsl_anat_nii_selection$voxel_volume, "^[:digit:]+(?= )") %>% as.numeric()
fsl_anat_nii_selection$volume <- str_extract(fsl_anat_nii_selection$voxel_volume, "(?<= )[:digit:]+\\.[:digit:]+") %>% as.numeric()

```


```{r}
library(forcats)
mask_madness <- fsl_anat_nii_selection %>%
  select(T1_brain_mask, id, session, voxel_n) %>%
  mutate(pipeline = str_extract(T1_brain_mask, "anat_[:graph:]+(?=_BET_05)") %>% str_replace("anat_", ""),
         type = str_replace(pipeline, "^T1$|T1_defaced_(mri_|py)deface$", "raw"),
         type = str_replace(type, "^T1_reorient2std$|T1_r2std_defaced_(mri_|py)deface$", "reorient"),
         type = str_replace(type, "^T1_crop$|T1_cropped_defaced_(mri_|py)deface$",  "cropped"),
         defacing = str_replace(pipeline, "^T(1|1_crop|1_reorient2std)$", "T1"),
         defacing = str_replace(defacing, "^T(1|1_cropped|1_r2std)_defaced_mri_deface$", "MRI_deface"),
         defacing = str_replace(defacing, "^T(1|1_cropped|1_r2std)_defaced_pydeface$", "Pydeface"),
         type = fct_relevel(type, c("raw", "reorient", "cropped")),
         defacing = fct_relevel(defacing, c("T1", "MRI_deface", "Pydeface"))) 

unique(mask_madness$type)
```



```{r}
library(ggplot2)

mask_madness %>%
  ggplot(aes(x = session, y = voxel_n)) +
  geom_boxplot() +
  facet_grid(type ~ defacing)
```

## Mean mask calculation

- add all masks up (voxel values of 0 - 9 )
- multiply end mask with 0.9


```{r}
mask_madness_input <- mask_madness %>% 
  select(id, session, pipeline, T1_brain_mask) %>%
  spread(pipeline, T1_brain_mask) %>%
  mutate(output_native = paste0("/media/niklas/spaceC/WML121_BIDS/derivatives/FSL/3-FSL_pipeline//mean_masks/", id, "_", session, "_mean_mask_native.nii.gz"),
         output_cropped = paste0("/media/niklas/spaceC/WML121_BIDS/derivatives/FSL/3-FSL_pipeline//mean_masks/", id, "_", session, "_mean_mask_cropped.nii.gz"),
         output = paste0("/media/niklas/spaceC/WML121_BIDS/derivatives/FSL/3-FSL_pipeline//mean_masks/means/", id, "_", session, "_mean_mask_cropped.nii.gz"),
         flirt_output = paste0("/media/niklas/spaceC/WML121_BIDS/derivatives/FSL/3-FSL_pipeline//mean_masks/flirt/", id, "_", session, "_mean_mask_flirt.nii.gz"),
         mask_differences = paste0("/media/niklas/spaceC/WML121_BIDS/derivatives/FSL/3-FSL_pipeline//mean_masks/means_thresholded/", id, "_", session, "_mean_mask_sub_1.nii.gz"))

dir.create("/media/niklas/spaceC/WML121_BIDS/derivatives/FSL/3-FSL_pipeline//mean_masks/")



mask_madness_input



create_mean_mask_native(mask_madness_input$T1, 
                        mask_madness_input$T1_reorient2std, 
                        mask_madness_input$T1_defaced_mri_deface, 
                        mask_madness_input$T1_defaced_pydeface,
                        mask_madness_input$T1_r2std_defaced_mri_deface, 
                        mask_madness_input$T1_r2std_defaced_pydeface,
                        output = mask_madness_input$output_native)

create_mean_mask_cropped(mask_madness_input$T1_crop,
                         mask_madness_input$T1_cropped_defaced_mri_deface,
                         mask_madness_input$T1_cropped_defaced_pydeface,
                         mask_madness_input$output_cropped)




```

# Problem T1 is another space, than reorient2std
```{r}
dir.create("/media/niklas/spaceC/WML121_BIDS/derivatives/FSL/3-FSL_pipeline//mean_masks/flirt/")

flirt_files(mask_madness_input$output_native,
            mask_madness_input$output_cropped,
            mask_madness_input$flirt_output)
```

```{r}
dir.create("/media/niklas/spaceC/WML121_BIDS/derivatives/FSL/3-FSL_pipeline//mean_masks/means/")

create_mean_mask(mask_madness_input$output_cropped,
                 mask_madness_input$flirt_output,
                 mask_madness_input$output)



```

# Now the masks exists (values between 0, 1 and 9)

 now we "threshold" the map, so that 9 is removed (so every region where every algorithm detected brain tissue)

```{r}
# standardize image
divide_number(mask_madness_input$output, 9, mask_madness_input$output )


dir.create("/media/niklas/spaceC/WML121_BIDS/derivatives/FSL/3-FSL_pipeline//mean_masks/means_thresholded/")

subtract_number(mask_madness_input$output, 1, )
```

