---
title: "fsl_pre_BIANCA"
author: "Niklas Wulms"
date: "7/27/2020"
output: html_document
---

```{r setup, include=FALSE}
library(stringr)
library(doParallel)
library(foreach)
library(tidyr)
library(dplyr)
library(logger)

source("fsl_flirt.R")
source("fsl_bet.R")
source("fsl_BIANCA.r")
source("../../functions/general.R")

knitr::opts_chunk$set(echo = TRUE)

working_dir <- "/mnt/Vierer/BIDS/derivatives_temp/FSL/"
knitr::opts_knit$set(root.dir = working_dir)
setwd(working_dir)
```

# Pipeline 1

- native
- defacing
- fsl_anat
- bet
- flirt

## inputs

### T1w

#### 1
- T1w -> fsl_anat [biascorr] -> bet 0.5

#### 2
- T1w -> fsldeface -> fsl_anat [biascorr} -> bet 0.5

### T2FLAIR

#### 1
- FLAIR -> bet 0.4 

#### 2
- FLAIR -> fsl_anat [biascorr] -> bet 0.4

## target output

- bias-corrected, brain-extracted T1w
- bias-corrected, brain-extracted T1w (FLAIR-space)
- bias-corrected, brain-extracted FLAIR
- bias-corrected, brain-extracted FLAIR (T1-space)

# indexing files

```{r}
nii_anat <- list.files(path = "/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_anat_pipeline/", 
                              pattern = ".nii|.mat", 
                              full.names = TRUE, 
                              recursive = TRUE)
nii_deface_anat <- list.files(path = "/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_deface_anat_pipeline", 
                              pattern = ".nii|.mat", 
                              full.names = TRUE, 
                              recursive = TRUE)

nii_deface <- list.files(path = "/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_deface_pipeline", 
                              pattern = ".nii|.mat", 
                              full.names = TRUE, 
                              recursive = TRUE)



nii_masks <- list.files(path = "/mnt/backup2/WML121_BIDS/derivatives", 
                              pattern = "FLAIR_mask_T2_space.nii", 
                              full.names = TRUE, 
                              recursive = TRUE)
```


```{r}
# input
T1w = str_subset(nii_anat, pattern = "T1w.nii.gz")
FLAIR = str_subset(nii_anat, pattern = "FLAIR.nii.gz")
T1w_deface = str_subset(nii_deface, pattern = "T1w_fsldeface.nii.gz")

# FSL_anat: bias-corrected
T1w_bc = str_subset(nii_anat, pattern = "T1_biascorr.nii.gz")
FLAIR_bc = str_subset(nii_anat, pattern = "T2_biascorr.nii.gz")
T1w_deface_bc = str_subset(nii_deface_anat, pattern = "T1_biascorr.nii.gz")

# BET
T1w_bc_bet = str_subset(nii_anat, pattern = "T1_biascorr_bet_0.5.nii.gz") # missing!
FLAIR_bc_bet = str_subset(nii_anat, pattern = "T2_biascorr_bet_0.4.nii.gz")
T1w_deface_bc_bet = str_subset(nii_deface_anat, pattern = "T1_biascorr_bet_0.5.nii.gz")

# matrices - MNI
T1w_to_mni_mat = str_subset(nii_anat, pattern = "T1_to_MNI_lin.mat")
T1w_deface_to_mni_mat = str_subset(nii_deface_anat, pattern = "T1_to_MNI_lin.mat")


```

```{r}
out_T1w <- str_replace(T1w, "fsl_anat_pipeline", "fsl_bianca_pipeline2/input")
out_FLAIR <- str_replace(FLAIR, "fsl_anat_pipeline", "fsl_bianca_pipeline2/input")
out_T1w_deface <- str_replace(T1w_deface, "fsl_deface_pipeline", "fsl_bianca_pipeline2/input")

out_T1w_bc <- str_replace(T1w_bc, "fsl_anat_pipeline", "fsl_bianca_pipeline2/bc") %>% 
  str_remove("/T1w.anat")
out_FLAIR_bc <- str_replace(FLAIR_bc, "fsl_anat_pipeline", "fsl_bianca_pipeline2/bc") %>% 
  str_remove("/FLAIR.anat")
out_T1w_deface_bc <- str_replace(T1w_deface_bc, "fsl_deface_anat_pipeline", "fsl_bianca_pipeline2/bc") %>% 
  str_remove("/T1w.anat") %>%
  str_replace("T1_biascorr", "T1_deface_biascorr")

out_T1w_bc_bet <- str_replace(T1w_bc_bet, "fsl_anat_pipeline", "fsl_bianca_pipeline2/bet") %>%
  str_remove("/T1w.anat")
out_FLAIR_bc_bet <- str_replace(FLAIR_bc_bet, "fsl_anat_pipeline", "fsl_bianca_pipeline2/bet")  %>% 
  str_remove("/FLAIR.anat")
out_T1w_deface_bc_bet <- str_replace(T1w_deface_bc_bet, "fsl_deface_anat_pipeline", "fsl_bianca_pipeline2/bet") %>% 
  str_remove("/T1w.anat") %>%
  str_replace("T1_biascorr", "T1_deface_biascorr")

out_T1w_to_mni_mat <- str_replace(T1w_to_mni_mat, "fsl_anat_pipeline", "fsl_bianca_pipeline2/matrices") %>%
  str_remove("/T1w.anat")
out_T1w_deface_to_mni_mat <- str_replace(T1w_deface_to_mni_mat, "fsl_deface_anat_pipeline", "fsl_bianca_pipeline2/matrices") %>% 
  str_remove("/T1w.anat") %>%
  str_replace("to_MNI_lin.mat", "deface_to_MNI_lin.mat")

out_FLAIR_mask <- str_replace(nii_masks, "/mnt/backup2/WML121_BIDS/derivatives/FSL/5-FSL_FLIRT/manual/", "/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline2/masks/")

```

```{r}
# Copy the relevant files
file_copy(T1w, out_T1w)
file_copy(FLAIR, out_FLAIR)
file_copy(T1w_deface, out_T1w_deface)

file_copy(T1w_bc, out_T1w_bc)
file_copy(FLAIR_bc, out_FLAIR_bc)
file_copy(T1w_deface_bc, out_T1w_deface_bc)

file_copy(T1w_bc_bet, out_T1w_bc_bet)
file_copy(FLAIR_bc_bet, out_FLAIR_bc_bet)
file_copy(T1w_deface_bc_bet, out_T1w_deface_bc_bet)

file_copy(T1w_to_mni_mat, out_T1w_to_mni_mat)
file_copy(T1w_deface_to_mni_mat, out_T1w_deface_to_mni_mat)

file_copy(nii_masks, out_FLAIR_mask)
```


# FLIRT

```{r}
# Step 1: removing of non-existing pairs (FLAIR less images than T1w)
out_FLAIR_bc_bet_exist <- str_replace(out_T1w_bc_bet, "T1", "T2") %>% str_replace("bet_0.5", "bet_0.4")

FLAIR_bc_bet_clean <- out_FLAIR_bc_bet_exist[file.exists(out_FLAIR_bc_bet_exist)]

T1w_bc_bet_clean <- out_T1w_bc_bet[file.exists(out_FLAIR_bc_bet_exist)]
T1w_deface_bc_bet_clean <- out_T1w_deface_bc_bet[file.exists(out_FLAIR_bc_bet_exist)]
```

```{r}
fsl_flirt(input_volume = FLAIR_bc_bet_clean,
          input_reference = T1w_bc_bet_clean, 
          prefix = "T1_space", 
          dof = 6)



fsl_flirt(input_volume = FLAIR_bc_bet_clean,
          input_reference = T1w_deface_bc_bet_clean, 
          prefix = "T1_deface_space", 
          dof = 6)


```

# Invert matrices

```{r}
mat_files <- list.files("/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline2/bet/", "_6.mat", recursive = TRUE, full.names = TRUE)
mat_files_output <- str_replace(mat_files, "fsl_bianca_pipeline2/bet", "fsl_bianca_pipeline2/matrices")
```


```{r}
file.rename(mat_files, mat_files_output)

fsl_convert_xfm(mat_files_output)
```


# T1 to T2 space

```{r}
inverse_FLAIR_bc_bet_to_T1w_bc_mat <- str_replace(out_T1w_to_mni_mat, "T1_to_MNI_lin", "T2_biascorr_bet_0.4_T1_space_6_inverse")
inverse_FLAIR_bc_bet_to_T1w_bc_deface_mat <- str_replace(out_T1w_deface_to_mni_mat, "T1_deface_to_MNI_lin", "T2_biascorr_bet_0.4_T1_deface_space_6_inverse")

bc_bet <- 
  tibble(T1 = T1w_bc_bet_clean,
       FLAIR = FLAIR_bc_bet_clean,
       T1_to_FLAIR_mat = inverse_FLAIR_bc_bet_to_T1w_bc_mat[file.exists(inverse_FLAIR_bc_bet_to_T1w_bc_mat)])

bc_bet_deface <- 
  tibble(T1 = T1w_deface_bc_bet_clean,
       FLAIR = FLAIR_bc_bet_clean,
       T1_to_FLAIR_mat = inverse_FLAIR_bc_bet_to_T1w_bc_deface_mat[file.exists(inverse_FLAIR_bc_bet_to_T1w_bc_deface_mat)])
```


```{r}
fsl_flirt_to_space(input_nii = T1w_bc_bet_clean,
                   input_ref = FLAIR_bc_bet_clean,
                   input_mat = inverse_FLAIR_bc_bet_to_T1w_bc_mat[file.exists(inverse_FLAIR_bc_bet_to_T1w_bc_mat)],
                   prefix = "_FLAIR_anat_space")

fsl_flirt_to_space(input_nii = T1w_deface_bc_bet_clean,
                   input_ref = FLAIR_bc_bet_clean,
                   input_mat = inverse_FLAIR_bc_bet_to_T1w_bc_deface_mat[file.exists(inverse_FLAIR_bc_bet_to_T1w_bc_deface_mat)],
                   prefix = "_FLAIR_anat_deface_space")
```



# Maskierung T2_bc Image mit T1_BET (T2-space) Image

```{r}
T1w_T2w_bc_T1w_inverse <- list.files("/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline2/bet/", 
                                        "T1_biascorr_bet_0.5_FLAIR_anat_space.nii.gz",
                                           recursive = TRUE, full.names = TRUE) 
T1w_T2w_bc_T1w_deface_inverse <- list.files("/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline2/bet/",
                                                   "T1_deface_biascorr_bet_0.5_FLAIR_anat_deface_space.nii.gz",
                                                recursive = TRUE, full.names = TRUE)

FLAIR_bc_clean <- out_FLAIR_bc[file.exists(out_FLAIR_bc_bet_exist)]
```


```{r}
fslmaths_mask(input_nii = FLAIR_bc_clean, input_mask = T1w_T2w_bc_T1w_inverse)
fslmaths_mask(input_nii = FLAIR_bc_clean, input_mask = T1w_T2w_bc_T1w_deface_inverse)
```


# T2 to MNI space (T2_to_T1_mat + T1_to_MNI_mat)

```{r}
# Indicate mat files
FLAIR_bc_bet_to_T1w_bc_mat <- str_replace(out_T1w_to_mni_mat, "T1_to_MNI_lin", "T2_biascorr_bet_0.4_T1_space_6")
FLAIR_bc_bet_to_T1w_bc_deface_mat <- str_replace(out_T1w_deface_to_mni_mat, "T1_deface_to_MNI_lin", "T2_biascorr_bet_0.4_T1_deface_space_6")
```


```{r}
# T2_to_T1_mat + T1_to_MNI_mat
fsl_convert_xfm_add_masks(input_mat1 = FLAIR_bc_bet_to_T1w_bc_mat[file.exists(FLAIR_bc_bet_to_T1w_bc_mat)],
                          input_mat2 = out_T1w_to_mni_mat[file.exists(FLAIR_bc_bet_to_T1w_bc_mat)])
fsl_convert_xfm_add_masks(input_mat1 = FLAIR_bc_bet_to_T1w_bc_deface_mat[file.exists(FLAIR_bc_bet_to_T1w_bc_deface_mat)],
                          input_mat2 = out_T1w_deface_to_mni_mat[file.exists(FLAIR_bc_bet_to_T1w_bc_deface_mat)])
```


# Creation of csv files

```{r}
# find T2 to MNI mats
T2_to_MNI_mat <- list.files("/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline2/matrices//", 
                                        "T1_space_6_FLAIR_to_MNI",
                                           recursive = TRUE, full.names = TRUE) 
T2_to_MNI_deface_mat <- list.files("/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline2/matrices//",
                                                   "T1_deface_space_6_FLAIR_to_MNI",
                                                recursive = TRUE, full.names = TRUE)


# FLAIR_bc_bet_clean (BET on FLAIR)
bc_bet <- 
  tibble(T1 = T1w_T2w_bc_T1w_inverse,
       FLAIR = FLAIR_bc_bet_clean,
       FLAIR_to_MNI_mat = T2_to_MNI_mat) %>%
  mutate(subject = str_extract(T1, "sub-[:digit:]{5}"),
         session = str_extract(T1, "ses-s[:digit:]{1}"),
         subject_session = paste0(subject, "_", session))

bc_bet_deface <- 
  tibble(T1 = T1w_T2w_bc_T1w_deface_inverse,
       FLAIR = FLAIR_bc_bet_clean,
       FLAIR_to_MNI_mat = T2_to_MNI_deface_mat) %>%
  mutate(subject = str_extract(T1, "sub-[:digit:]{5}"),
         session = str_extract(T1, "ses-s[:digit:]{1}"),
         subject_session = paste0(subject, "_", session))

# FLAIR_bc_clean (T1_BET masked FLAIR)
FLAIR_bc_bet_T1w_masked <- list.files("/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline2/bet/", 
                                        "FLAIR_T1w_space_biascorr_bet_0.5_FLAIR_anat_space.nii.gz",
                                           recursive = TRUE, full.names = TRUE) 
FLAIR_bc_bet_T1w_defaced_masked <- list.files("/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline2/bet/",
                                                   "FLAIR_T1w_space_deface_biascorr_bet_0.5_FLAIR_anat_deface_space.nii.gz",
                                                recursive = TRUE, full.names = TRUE)

bc_bet_clean <- 
  tibble(T1 = T1w_T2w_bc_T1w_inverse,
       FLAIR = FLAIR_bc_bet_T1w_masked,
       FLAIR_to_MNI_mat = T2_to_MNI_mat) %>%
  mutate(subject = str_extract(T1, "sub-[:digit:]{5}"),
         session = str_extract(T1, "ses-s[:digit:]{1}"),
         subject_session = paste0(subject, "_", session))

bc_bet_deface_clean <- 
  tibble(T1 = T1w_T2w_bc_T1w_deface_inverse,
       FLAIR = FLAIR_bc_bet_T1w_defaced_masked,
       FLAIR_to_MNI_mat = T2_to_MNI_deface_mat) %>%
  mutate(subject = str_extract(T1, "sub-[:digit:]{5}"),
         session = str_extract(T1, "ses-s[:digit:]{1}"),
         subject_session = paste0(subject, "_", session))
```

# Training & Test sets

## creation



```{r}
# training sets (121 - s4)
bc_bet %>%
  filter(subject_session %in% subjects_masks) %>%
  mutate(lesion_mask = out_FLAIR_mask) %>%
  filter(str_detect(subject_session, "ses-s4")) %>%
  select(FLAIR, T1, FLAIR_to_MNI_mat, lesion_mask) %>%
  write.table(file="/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline2/model_csv/bc_bet_121_train.txt", quote=FALSE, sep='\t', col.names = FALSE, row.names = FALSE)

bc_bet_deface %>%
  filter(subject_session %in% subjects_masks) %>%
  mutate(lesion_mask = out_FLAIR_mask) %>%
  filter(str_detect(subject_session, "ses-s4")) %>%
  select(FLAIR, T1, FLAIR_to_MNI_mat, lesion_mask) %>%
  write.table(file="/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline2/model_csv/bc_bet_deface_121_train.txt", quote=FALSE, sep='\t', col.names = FALSE, row.names = FALSE)

bc_bet_clean %>%
  filter(subject_session %in% subjects_masks) %>%
  mutate(lesion_mask = out_FLAIR_mask) %>%
  filter(str_detect(subject_session, "ses-s4")) %>%
  select(FLAIR, T1, FLAIR_to_MNI_mat, lesion_mask) %>%
  write.table(file="/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline2/model_csv/bc_bet_clean_121_train.txt", quote=FALSE, sep='\t', col.names = FALSE, row.names = FALSE)

bc_bet_deface_clean %>%
  filter(subject_session %in% subjects_masks) %>%
  mutate(lesion_mask = out_FLAIR_mask) %>%
  filter(str_detect(subject_session, "ses-s4")) %>%
  select(FLAIR, T1, FLAIR_to_MNI_mat, lesion_mask) %>%
  write.table(file="/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline2/model_csv/bc_bet_deface_clean_121_train.txt", quote=FALSE, sep='\t', col.names = FALSE, row.names = FALSE)


# test sets
subjects_masks <- str_extract(out_FLAIR_mask, "sub-[:digit:]{5}_ses-S[:digit:]{1}") %>%
  str_replace("ses-S", "ses-s")

# filtered csv with known subjects
bc_bet %>%
  filter(subject_session %in% subjects_masks) %>%
  select(FLAIR, T1, FLAIR_to_MNI_mat) %>%
  write.table(file="/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline2/model_csv/bc_bet_201.txt", quote=FALSE, sep='\t', col.names = FALSE, row.names = FALSE)

bc_bet_deface %>%
  filter(subject_session %in% subjects_masks) %>%
  select(FLAIR, T1, FLAIR_to_MNI_mat) %>%
  write.table(file="/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline2/model_csv/bc_bet_deface_201.txt", quote=FALSE, sep='\t', col.names = FALSE, row.names = FALSE)

bc_bet_clean %>%
  filter(subject_session %in% subjects_masks) %>%
  select(FLAIR, T1, FLAIR_to_MNI_mat) %>%
  write.table(file="/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline2/model_csv/bc_bet_clean_201.txt", quote=FALSE, sep='\t', col.names = FALSE, row.names = FALSE)

bc_bet_deface_clean %>%
  filter(subject_session %in% subjects_masks) %>%
  select(FLAIR, T1, FLAIR_to_MNI_mat) %>%
  write.table(file="/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline2/model_csv/bc_bet_deface_clean_201.txt", quote=FALSE, sep='\t', col.names = FALSE, row.names = FALSE)

# filtered csv with ALL subjects
bc_bet %>%
  select(FLAIR, T1, FLAIR_to_MNI_mat) %>%
  write.table(file="/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline2/model_csv/bc_bet.txt", quote=FALSE, sep='\t', col.names = FALSE, row.names = FALSE)

bc_bet_deface %>%
  select(FLAIR, T1, FLAIR_to_MNI_mat) %>%
  write.table(file="/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline2/model_csv/bc_bet_deface.txt", quote=FALSE, sep='\t', col.names = FALSE, row.names = FALSE)

bc_bet_clean %>%
  select(FLAIR, T1, FLAIR_to_MNI_mat) %>%
  write.table(file="/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline2/model_csv/bc_bet_clean.txt", quote=FALSE, sep='\t', col.names = FALSE, row.names = FALSE)

bc_bet_deface_clean %>%
  select(FLAIR, T1, FLAIR_to_MNI_mat) %>%
  write.table(file="/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline2/model_csv/bc_bet_deface_clean.txt", quote=FALSE, sep='\t', col.names = FALSE, row.names = FALSE)
```



## LOO models

```{r}
# a <- list.files(path = "/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline2/bet/", pattern = "mask", full.names = TRUE, recursive = TRUE)
# file.remove(a)
library(readr)
bianca_r(masterfile = "/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline2/model_csv/bc_bet_121_train.txt",
         model_name = "bc_bet_121")
bianca_r(masterfile = "/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline2/model_csv/bc_bet_deface_121_train.txt",
         model_name = "bc_bet_deface_121")
bianca_r(masterfile = "/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline2/model_csv/bc_bet_clean_121_train.txt",
         model_name = "bc_bet_clean_121")
bianca_r(masterfile = "/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline2/model_csv/bc_bet_deface_clean_121_train.txt",
         model_name = "bc_bet_deface_clean_121")
```


## training

```{r}
classifier_1 <- "/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline2/model_csv/bc_bet_121_model"
classifier_2 <- "/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline2/model_csv/bc_bet_deface_121_model"
classifier_3 <- "/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline2/model_csv/bc_bet_clean_121_model"
classifier_4 <- "/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline2/model_csv/bc_bet_deface_clean_121_model"
```



```{r}


train_bianca(masterfile = "/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline2/model_csv/bc_bet_121_train.txt",
             output_name = "/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline2/model_csv/output1.nii",
             output_classifier = "/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline2/model_csv/bc_bet_121_model")

train_bianca(masterfile = "/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline2/model_csv/bc_bet_deface_121_train.txt",
             output_name = "/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline2/model_csv/output1.nii",
             output_classifier = "/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline2/model_csv/bc_bet_deface_121_model")

train_bianca(masterfile = "/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline2/model_csv/bc_bet_clean_121_train.txt",
             output_name = "/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline2/model_csv/output1.nii",
             output_classifier = "/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline2/model_csv/bc_bet_clean_121_model")

train_bianca(masterfile = "/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline2/model_csv/bc_bet_deface_clean_121_train.txt",
             output_name = "/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline2/model_csv/output1.nii",
             output_classifier = "/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline2/model_csv/bc_bet_deface_clean_121_model")
```



# BIACA Prediction

## New stuff

```{r}
model121 <- "/home/niklas/Owncloud/wulms/BiDirect_Neuroimaging/BIANCA_classifier/output_classifier_121"
model201 <- "/home/niklas/Owncloud/wulms/BiDirect_Neuroimaging/BIANCA_classifier/output_classifier_201"
```

```{r}
bianca_folder <- "/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline2/model_csv/"

bianca_file_1 <- paste0(bianca_folder, "bc_bet.txt")
bianca_file_2 <- paste0(bianca_folder, "bc_bet_deface.txt")
bianca_file_3 <- paste0(bianca_folder, "bc_bet_clean.txt")
bianca_file_4 <- paste0(bianca_folder, "bc_bet_deface_clean.txt")
```

## Artefacts

```{r}
application_bianca_classifiers(trained_models = c(classifier_1), 
                               test_sets = bianca_file_1,
                               prefix = "bc_bet_new")

application_bianca_classifiers(trained_models = c(classifier_2), 
                               test_sets = bianca_file_3,
                               prefix = "bc_bet_deface_new")

application_bianca_classifiers(trained_models = c(classifier_3), 
                               test_sets = bianca_file_2,
                               prefix = "bc_bet_clean_new")

application_bianca_classifiers(trained_models = c(classifier_4), 
                               test_sets = bianca_file_4,
                               prefix = "bc_bet_deface_clean_new")
```

```{r}
# first models
pipeline9 <- list.files("/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline/model_121/", ".nii", recursive = TRUE, full.names = TRUE)
pipeline10 <- list.files("/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline/model_121_deface_anat/", ".nii", recursive = TRUE, full.names = TRUE)
pipeline11 <- list.files("/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline/model_121_deface_bc_anat/", ".nii", recursive = TRUE, full.names = TRUE)

# old
pipeline1 <- list.files("/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline/bc_bet/", ".nii", recursive = TRUE, full.names = TRUE)
pipeline2 <- list.files("/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline/bc_bet_clean/", ".nii", recursive = TRUE, full.names = TRUE)
pipeline3 <- list.files("/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline/bc_bet_deface/", ".nii", recursive = TRUE, full.names = TRUE)
pipeline4 <- list.files("/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline/bc_bet_deface_clean/", ".nii", recursive = TRUE, full.names = TRUE)

# new
pipeline5 <- list.files("/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline/bc_bet_new/", ".nii", recursive = TRUE, full.names = TRUE)
pipeline6 <- list.files("/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline/bc_bet_clean_new/", ".nii", recursive = TRUE, full.names = TRUE)
pipeline7 <- list.files("/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline/bc_bet_deface_new/", ".nii", recursive = TRUE, full.names = TRUE)
pipeline8 <- list.files("/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline/bc_bet_deface_clean_new/", ".nii", recursive = TRUE, full.names = TRUE)

```

```{r}
bianca_cluster_info(pipeline1, threshold = 0.7)
bianca_cluster_info(pipeline2, threshold = 0.7)
bianca_cluster_info(pipeline3, threshold = 0.7)
bianca_cluster_info(pipeline4, threshold = 0.7)

bianca_cluster_info(pipeline5, threshold = 0.8)
bianca_cluster_info(pipeline6, threshold = 0.8)
bianca_cluster_info(pipeline7, threshold = 0.8)
bianca_cluster_info(pipeline8, threshold = 0.8)

bianca_cluster_info(pipeline9, threshold = 0.7)
bianca_cluster_info(pipeline10, threshold = 0.7)
bianca_cluster_info(pipeline11, threshold = 0.7)
```


# Volume extraction

```{r}
bianca_txt_files <- list.files("/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline/", "mask_0.(7|8).txt", recursive = TRUE, full.names = TRUE)

models <- tibble(subject = str_extract(bianca_txt_files,  "sub-[:digit:]{5}"),
                 session = str_extract(bianca_txt_files, "ses-s[:digit:]{1}"),
                 model = str_remove(bianca_txt_files, "/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline/") %>%
                   str_extract("[:graph:]*(?=sub-[:digit:]{5}/ses-s[:digit:]{1}/)") %>%
                   str_remove_all("/"),
                 threshold = str_extract(bianca_txt_files, "mask_[:graph:]*$") %>% str_extract("0.[:digit:]+(?=.txt)"),
                 wmh_number = lapply(bianca_txt_files, volume_extractor, "wmh_number") %>% unlist() %>% as.numeric(),
                 wmh_volume = lapply(bianca_txt_files, volume_extractor, "total_wmh_volume") %>% unlist() %>% as.numeric())

readr::write_csv(models, path = "/home/niklas/Owncloud/wulms/BD_variablen/neuroimaging/bianca_model_s4_121_pipelines.csv")

```


```{r}
pipeline1txt <- list.files("/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline/bc_bet_new/", ".txt", recursive = TRUE, full.names = TRUE)
pipeline2txt <- list.files("/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline/bc_bet_clean_new/", ".txt", recursive = TRUE, full.names = TRUE)
pipeline3txt <- list.files("/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline/bc_bet_deface_new/", ".txt", recursive = TRUE, full.names = TRUE)
pipeline4txt <- list.files("/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline/bc_bet_deface_clean_new/", ".txt", recursive = TRUE, full.names = TRUE)


model121_deface_anat <- tibble(subject = str_extract(pipeline1txt, "sub-[:digit:]{5}"),
       session = str_extract(pipeline1txt, "ses-s[:digit:]{1}"),
       wmh_number1 = lapply(pipeline1txt, volume_extractor, "wmh_number") %>% unlist() %>% as.numeric(),
       wmh_volume1 = lapply(pipeline1txt, volume_extractor, "total_wmh_volume") %>% unlist() %>% as.numeric(),
       wmh_number2 = lapply(pipeline2txt, volume_extractor, "wmh_number") %>% unlist() %>% as.numeric(),
       wmh_volume2 = lapply(pipeline2txt, volume_extractor, "total_wmh_volume") %>% unlist() %>% as.numeric(),
       wmh_number3 = lapply(pipeline3txt, volume_extractor, "wmh_number") %>% unlist() %>% as.numeric(),
       wmh_volume3 = lapply(pipeline3txt, volume_extractor, "total_wmh_volume") %>% unlist() %>% as.numeric(),
       wmh_number4 = lapply(pipeline4txt, volume_extractor, "wmh_number") %>% unlist() %>% as.numeric(),
       wmh_volume4 = lapply(pipeline4txt, volume_extractor, "total_wmh_volume") %>% unlist() %>% as.numeric())


readr::write_csv(model121_deface_anat, path = "/home/niklas/Owncloud/wulms/BD_variablen/neuroimaging/bianca_pipelines4.csv")

# manual_maskstxt <- list.files("/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bianca_pipeline2/masks/", ".txt", recursive = TRUE, full.names = TRUE)
# 
# masks_df <- tibble(subject = str_extract(manual_maskstxt, "sub-[:digit:]{5}"),
#        session = str_extract(manual_maskstxt, "ses-S[:digit:]{1}") %>% str_replace("S", "s"),
#        wmh_number1 = lapply(manual_maskstxt, volume_extractor, "wmh_number") %>% unlist() %>% as.numeric(),
#        wmh_volume1 = lapply(manual_maskstxt, volume_extractor, "total_wmh_volume") %>% unlist() %>% as.numeric())
       
# readr::write_csv(masks_df, path = "/home/niklas/Owncloud/wulms/BD_variablen/neuroimaging/manual_masks.csv")
```


```{r}
```

```{r}
library(ggplot2)

model121_deface_anat %>%
  ggplot(aes(x = wmh_number1, y = wmh_number2)) +
  geom_point()

model121_deface_anat %>%
  ggplot(aes(x = wmh_number3, y = wmh_number4)) +
  geom_point()


```

