---
title: "FSL FLIRT"
author: "Niklas Wulms"
date: "4/22/2020"
output: html_document
---

```{r setup, include=FALSE}
library(stringr)
library(doParallel)
library(foreach)
library(tidyr)
library(dplyr)

source("fsl_flirt.R")
source("fsl_bet.R")
source("../../functions/general.R")

knitr::opts_chunk$set(echo = TRUE)

working_dir <- "/mnt/Vierer/BIDS/derivatives_temp/FSL/"
knitr::opts_knit$set(root.dir = working_dir)
setwd(working_dir)
```

# Bet of T2 (errors in fsl_anat pipeline)


```{r}
fsl_anat_nii_selection_t2 <- data.frame(
  # raw input and first preprocs
  T2_biascorr = list.files("/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_anat_pipeline/", "T2_biascorr.nii.gz", recursive = TRUE, full.names = TRUE),
  stringsAsFactors = F)             

fsl_anat_nii_selection_t2  
```

```{r}
fsl_bet(fsl_anat_nii_selection_t2$T2_biascorr,
        fval=seq(0.3, 0.7, 0.2))
```



# Flirt of processed BET images

```{r}
nii_files <- tibble(
  # raw input and first preprocs
  T2_biascorr_BET  = list.files("/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_bet_pipeline/", 
                                "T2_0.5_biascorr.nii.gz", recursive = TRUE, full.names = TRUE),
  T1_BET = str_replace(T2_biascorr_BET, "fsl_bet_pipeline",  "fsl_anat_pipeline") %>%
    str_replace("T2_0.5_biascorr.nii.gz", "T1_biascorr_brain.nii.gz") %>%
    str_replace("FLAIR.anat", "T1w.anat"),
  T2_biascorr  = str_replace(T2_biascorr_BET, "fsl_bet_pipeline",  "fsl_anat_pipeline") %>%
    str_replace("T2_0.5_biascorr.nii.gz", "T2_biascorr.nii.gz")
  )             

nii_files  
```


```{r}
fsl_flirt(input_volume = nii_files$T2_biascorr_BET,
          input_reference = nii_files$T1_BET, 
          prefix = "T1_space", 
          dof = 6)

fsl_flirt(input_volume = nii_files$T2_biascorr_BET,
          input_reference = nii_files$T1_BET, 
          prefix = "T1_space", 
          dof = 12)
```



# Invert matrices

```{r}
mat_files <- list.files("/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_flirt_pipeline/", 
                                 "(12|6).mat", recursive = TRUE, full.names = TRUE)


# invert mat
fsl_convert_xfm(mat_files)
```

# Bringing MNI matrix to T2 space

```{r}
mat_files_T1_to_MNI <- list.files("/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_anat_pipeline/", 
                                "T1_to_MNI_lin.mat", recursive = TRUE, full.names = TRUE)
mat_files_06 <- list.files("/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_flirt_pipeline/", 
                                "_space_6.mat", recursive = TRUE, full.names = TRUE)
mat_files_12 <- list.files("/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_flirt_pipeline/", 
                                "_space_12.mat", recursive = TRUE, full.names = TRUE)
# due to inconsisten file numbers - renaming of mat_files_06

mat_files_to_MNI <- str_replace(mat_files_06, "fsl_flirt", "fsl_anat") %>%
  str_replace("FLAIR.anat", "T1w.anat") %>%
  str_replace("T2_0.5_biascorr_T1_space_6", "T1_to_MNI_lin")

# concatenate mat (FLAIR_to_T1, T1_to_MNI_lin-> 1 MAT)
fsl_convert_xfm_add_masks(input_mat1 = mat_files_06,
                          input_mat2 = mat_files_to_MNI)
fsl_convert_xfm_add_masks(input_mat1 = mat_files_12,
                          input_mat2 = mat_files_to_MNI)
```



```{r}
#file.rename(mat_files, mat_files_06)

mat_files <- data.frame(mat = list.files("/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_flirt_pipeline/", 
                                "_inverse", recursive = TRUE, full.names = TRUE),
                        stringsAsFactors = FALSE)
head(mat_files)

mat_files <- mat_files %>%
  mutate(type = str_extract(mat, "(6|12)_inverse"),
         id = str_extract(mat, "sub-[:digit:]{5}/ses-s[:digit:]{1}")) %>%
  spread(type, mat)
```



# Apply inverted matrix to T1 image, to bring it in FLAIR space

Input: 
-T1_BET pydeface raw
-T1_BET fsldeface cropped

Template:
-T2_biascorr_BET

```{r}
output = str_replace(nii_files$T1_BET, ".nii", "_T2_space_6.nii") %>% str_replace("fsl_anat", "fsl_flirt")



fsl_flirt_to_space(input_nii = nii_files$T1_BET,
                   input_ref = nii_files$T2_biascorr_BET,
                   input_mat = mat_files$`6_inverse`,
                   output = output)

output = str_replace(nii_files$T1_BET, ".nii", "_T2_space_12.nii") %>% str_replace("fsl_anat", "fsl_flirt")


fsl_flirt_to_space(input_nii = nii_files$T1_BET,
                   input_ref = nii_files$T2_biascorr_BET,
                   input_mat = mat_files$`12_inverse`,
                   output = output)

```

# Mask the T2 images, with the high-res T1 image (that is flirted to T2 space)

```{r}
nii_inverse <- data.frame(mat = list.files("/mnt/Vierer/BIDS/derivatives_temp/FSL/fsl_flirt_pipeline/", 
                                "T2_space_(6|12).nii.gz", recursive = TRUE, full.names = TRUE),
                        stringsAsFactors = FALSE)
head(nii_inverse)

nii_inverse <- nii_inverse %>%
  mutate(type = str_extract(mat, "T2_space_(6|12)"),
         id = str_extract(mat, "sub-[:digit:]{5}/ses-s[:digit:]{1}")) %>%
  spread(type, mat)
head(nii_inverse)
```

# The T1 image is now in T2 space (using T2_BET and T1_BET for FLIRT, as well as the inverse transformation matrix)

Now, we want to apply the T1 BET mask to the T2 images, to enhance BET quality.

```{r}
fslmaths_mask(input_nii = nii_files$T2_biascorr,
              input_mask = nii_inverse$T2_space_6)
cat("\14")
fslmaths_mask(input_nii = nii_files$T2_biascorr,
              input_mask = nii_inverse$T2_space_12)

```

# Bringing FLAIR masks into T2_orig space

```{r}
nii_files <- data.frame(
  # raw input and first preprocs
  FLAIR = list.files("/mnt/458e8a35-865f-4f0e-ab7e-8b4ac8684363/WML121_BIDS/derivatives/FSL/3-FSL_pipeline/anat_FLAIR_defaced_pydeface/",
                                             "T2.nii.gz", recursive = TRUE, full.names = TRUE),
  FLAIR_mask = list.files("/mnt/458e8a35-865f-4f0e-ab7e-8b4ac8684363/WML121_BIDS/derivatives/manual/",
                                             "mask.nii.gz", recursive = TRUE, full.names = TRUE),
  FLAIR_to_FLAIR_orig  = list.files("/mnt/458e8a35-865f-4f0e-ab7e-8b4ac8684363/WML121_BIDS/derivatives/FSL/3-FSL_pipeline/anat_FLAIR_defaced_pydeface/", 
                                "T2_orig2std.mat", recursive = TRUE, full.names = TRUE),
  
  stringsAsFactors = F)             


output = str_replace(nii_files$FLAIR_mask, "manual", "FSL/5-FSL_FLIRT/manual") %>% str_replace("mask", "mask_T2_space") %>% str_replace("anat/", "")


```

```{r}
fsl_flirt_to_space(input_nii = nii_files$FLAIR_mask,
                   input_ref = nii_files$FLAIR,
                   input_mat = nii_files$FLAIR_to_FLAIR_orig,
                   output = output)
```








