---
title: "WML121_copy_all_data"
output: html_document
---


```{r setup, include=FALSE}
library(stringr)
library(doParallel)
library(foreach)
library(dplyr)
library(tidyr)

source("../../tools/path_to_folder.R")


knitr::opts_chunk$set(echo = TRUE)

working_dir <- "/media/niklas/My Book/Bidirect_Dicom/BIDS/base_protocol"
knitr::opts_knit$set(root.dir = working_dir)

setwd(working_dir)
```


setwd(working_dir)
```


```{r}
T1w <- list.files("/media/niklas/My Passport/WML121_BIDS/sourcedata", "T1w.nii.gz", recursive = TRUE, full.names = TRUE)

T1w_output <- T1w %>% 
  str_replace("Bidirect_Dicom/", "") %>%
  str_replace("BIDS", "BIDS/derivatives/SPM") %>%
  str_replace("nii.gz", "nii")

selected_subjects <- T1w %>%
  str_extract("sub-[:digit:]{5}_ses-S(0|4)") %>%
  str_replace_all("S0" , "1") %>%
  str_replace_all("S4", "3")
  
file2copy <- list.files(working_dir, pattern = paste(selected_subjects, collapse = "|"),
                 recursive = TRUE, full.names = TRUE)

  files2copy <- data.frame(inputs = file2copy,
                         short = str_extract(file2copy, "sub-[:digit:]{5}_ses-(1|3)"),
                         output = str_replace(file2copy, "My Book/Bidirect_Dicom/BIDS", "My Passport/WML121_BIDS_2"),
                         stringsAsFactors = FALSE)

files2copy %>%
  filter(
    
  )))

# Control if they exist
selected_subjects_BIDS <- unique(files2copy$short)

union(selected_subjects, selected_subjects_BIDS)


path_to_folder(files2copy$output)


relevant_files <- files2copy %>%
  filter(str_detect(inputs, "T1|flair|DTI"))
  #print(paste0("gunzip -c '", T1w[1], "' > '", T1w_output[1], "'"))  
```

# move files


```{r}
file.copy(relevant_files$input, relevant_files$output)
```

```{r}
library(R.utils)

for (i in 1:length(T1w)) {
  print(paste0("Data ", i, " of ", length(T1w)))
  gunzip(T1w[i], destname = T1w_output[i], remove=FALSE, skip = TRUE)
}
```